Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an empirical study of the Moran process for the iterated Prisoner's dilemma

### 2017-07-19 main.tex
Add affiliation and links to data.
Still need to reference ml paper once it's on the arxiv.

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{standalone}
\usepackage{fancyvrb}
\usepackage{algorithm,algorithmic}

@@

% Title
\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
       Mechanisms: an empirical study of the Moran process for the iterated
       Prisoner's dilemma using reinforcement learning}
\author{Vincent Knight \and
        Marc Harper \and
        Nikoleta E. Glynatsi \and
        Owen Campbell} % TODO Authors?
\date{}

@@

More information about each player can be obtained in the documentation for
\cite{axelrodproject} and a detailed description of the performance
 of these strategies in IPD tournaments will be described in upcoming manuscript(s).
% TODO Think of how to reference this upcoming manuscript

@@

% Todo: verify 1000 repetitions

@@

This section outlines the data analysis carried out:

>>>>

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{standalone}
\usepackage{fancyvrb}
\usepackage{algorithm,algorithmic}
\usepackage{authblk}

@@

% Title
\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
       Mechanisms: an empirical study of the Moran process for the iterated
       Prisoner's dilemma}
\author[1]{Vincent Knight}
\author[2]{Marc Harper}
\author[1]{Nikoleta E. Glynatsi}
\author[3]{Owen Campbell}

\affil[1]{Cardiff University, School of Mathematics, UK}
\affil[2]{Google Inc., Mountain View, CA, USA}
\affil[3]{Not affiliated}

\date{}

@@

More information about each player can be obtained in the documentation for
\cite{axelrodproject} and a detailed description of the performance
 of these strategies in IPD tournaments will be described in upcoming manuscript(s).
% TODO Reference ml paper on arxiv.

@@

@@

This section outlines the data analysis carried out, all data for this study is
available at~\cite{data}:
